---
title: "Team05Lab05"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Team05Lab05}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Team05Lab05)
```

# Lab05: A package connecting to a web API

For this lab, we created a package which connects to the carbon intensity API. You can follow this link to the [Carbon Intensity UK API](https://carbonintensity.org.uk/)  

## Getting to know the regions.  
The API connects to data from 17 different regions. You can see the regions [here](https://carbon-intensity.github.io/api-definitions/?python#region-list) or calling the regions() function.    
```{r, eval=TRUE}
    regions()  
```  

## Get the electricity sources used between specified datetimes for a specified region.  
The check_fuel_region_time function returns a dataframe with the fuels used in an interval of time. When calling the function, you have to add the following parameters.  

+ **region** A number (regionid) or a string (region short name). If nothing specified, the default is "Scotland". Call regions() to know the admitted values.   
+ **from** A string with shape yyyy-mm-ddTHH:mmZ, representing the start datetime.  
+ **to** A string with shape yyyy-mm-ddTHH:mmZ, representing the end datetime. The end date time can be max 1 month after **from** date

## Example
Using the following command  
```{r, eval=FALSE}
check_fuel_region_time("Scotland", "2018-11-16T09:00Z", "2018-12-10T16:00Z")
```  
we will get a data frame containing the fuels used between the time interval [from, to] in the specified region.  

```{r, eval=TRUE, echo = FALSE}
check_fuel_region_time("Scotland", "2018-11-16T09:00Z", "2018-12-10T16:00Z")
```  

## Plotting the electricity sources used between specified datetimes for a specified region.  
The pie_API_2 function returns a plot of the fuels used in an interval of time. When calling the function, you have to add the following parameters.  

+ **region** A number (regionid) or a string (region short name). If nothing specified, the default is "Scotland". Call regions() to know the admitted values.   
+ **from** A string with shape yyyy-mm-ddTHH:mmZ, representing the start datetime.  
+ **to** A string with shape yyyy-mm-ddTHH:mmZ, representing the end datetime. The end date time can be max 1 month after **from** date

## Example
Using the following command  

```{r, eval=FALSE}
pie_API_2("Scotland", "2018-11-16T09:00Z", "2018-12-10T16:00Z")
```  
  
we will get a plot of the fuels used between the time interval [from, to] in the specified region.  

```{r, eval=TRUE, echo = FALSE}
pie_API_2("Scotland", "2018-11-16T09:00Z", "2018-12-10T16:00Z")
```  